Interactive effects of drought and habitat fragmentation on vital rates of an understory tropical plant

### 2020-11-12 analysis/paper/paper.Rmd
remove Rubim as author, knit to Word

---
title: "Interactive effects of drought and habitat fragmentation on vital rates of an understory tropical plant"
author:
  - Eric R. Scott:
      email: scottericr@gmail.com
      institute: [UF]
      correspondence: true
  - Paulo Rubim:
      email: rubimpaulo@gmail.com
      institute: [UFSC]
      correspondence: false
  - Maria Uriarte:
      email: mu2126@columbia.edu
      institute: [Columbia]
      correspondence: false
  - Emilio M. Bruna:
      email: embruna@ufl.edu
      intitute: [UF]
      correspondence: false

institute:
  - UF: Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, Florida 32611-0430
  - UFSC: Departamento do Botânica, Universidade Federal de São Carlos, CP 676, CEP 13565-905, São Carlos, SP, Brazil
  - Columbia: Department of Ecology, Evolution and Environmental Biology, Columbia University 1200 Amsterdam Avenue, New York, New York 10027 USA
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/ecology.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  forest fragmentation; vital rates; *Heliconia acuminata*; drought; ENSO; edge effects
highlights: |
  These are the highlights
---

@@

>>>>

---
title: "Interactive effects of drought and habitat fragmentation on vital rates of an understory tropical plant"
author:
  - Eric R. Scott:
      email: scottericr@gmail.com
      institute: [UF]
      correspondence: true
  - Maria Uriarte:
      email: mu2126@columbia.edu
      institute: [Columbia]
      correspondence: false
  - Emilio M. Bruna:
      email: embruna@ufl.edu
      intitute: [UF]
      correspondence: false

institute:
  - UF: Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, Florida 32611-0430
  - Columbia: Department of Ecology, Evolution and Environmental Biology, Columbia University 1200 Amsterdam Avenue, New York, New York 10027 USA
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/ecology.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  forest fragmentation; vital rates; *Heliconia acuminata*; drought; ENSO; edge effects
highlights: |
  These are the highlights
---

@@

If TRMM data is used, they suggest: "The TMPA data were provided by the\
NASA/Goddard Space Flight Center's Mesoscale Atmospheric Processes Laboratory and\
PPS, which develop and compute the TMPA as a contribution to TRMM."
